---
title: "Weight of Fish"
author: "YErick Barraza"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
allthat <- read.csv(file = "Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch
```{r}
perch <- filter(allthat,Species=="Perch")
perch <- select(perch,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets( Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This perch model shows us that the best two plots to find the best weight is to use Height and Width.



```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

This model shows that the two best models are height and width since the model since it's true.

# Bream
```{r}
Bream <- filter(allthat,Species=="Bream")
Bream <- select(Bream,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets( Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

For the bream model, the two best plots are height and lenght 2 which is different from the first model.

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

The summary backs up the claim that Length 2 and Height are the two best plots for the bream model.


# Smelt
```{r}
Smelt<- filter(allthat,Species=="Smelt")
Smelt <- select(Smelt,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets( Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The smelt model shows that length 2 and width are the two best plots for Smelt.

```{r}
which.max(summary.out$adjr2)
```

```{r}
summary.out$which[2,]
```

This summary for SMelt confirms that Length 2 and Width are the best two plots.


# Conclusion

For this write-up, we had to create a regression model that would chose the best two plots in order to predict the weight of three fishes. The first fish was a preach in which we filter and selected preach fish for our data. This happened another two times for smelt and bream in order to plug it in our regression models. Then we ran the regression model which gave three different combinations between all three fish. Then we used the sumarry in order to check our model and see if the regression model was correct and had chose the two best plots for all three fish.